Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-10 paper.tex
Suite intro

\subsection{Discrete Optimal Transport}
We consider two discrete probability measures $\mu^k \in \IR_{+*}^{n_k}$.
Let us define the two following linear operators
\begin{align*}
A_1 &: \begin{cases}
\IR^{n_1 n_2} \rightarrow \IR^{n_1} \\
(A_1 x)_i = \sum_j x_{i,j}
\end{cases} &
A_2 &: \begin{cases}
\IR^{n_1 n_2} \rightarrow \IR^{n_2}\\
(A_2 x)_j = \sum_i x_{i,j},
\end{cases}
\end{align*}
as well as the linear  constraint sets
\begin{align*}
\Ccal_k &= \left\{ \gamma\in\IR^{n_1 n_2} \mid A_k \gamma = \mu^k \right\}.
\end{align*}
Given a cost matrix $c$, where $c_{ij}$ represents the cost of moving mass $\mu^1_i$ to $\mu^2_j$,  the optimal transport problem corresponds to the following minimization problem:
$$\min_{\gamma\in\Ccal_1\cap \Ccal_2\cap \IR^{n_1 n_2}_+} \langle c,\gamma\rangle:=\sum_{i,j}c_{i,j}\gamma_{i,j}.$$
This is a linear programing problem whose resolution is intractable for large scale problems.

@@

\subsection{Sinkhorn's algorithm}
Iterative Bregman projections onto $\Ccal_1$ and $\Ccal_2$ converge to a point in the intersection $\Ccal_1 \cap \Ccal_2$ \cite{bregman67}. Hence, the so-called Sinkhorn algorithm \cite{sinkhorn64} can be considered to compute the regularized  plan:
\begin{align*}
\gamma^0 &= e^{-c/\epsilon} &
\gamma^{l+1} = P_{\Ccal_2}(P_{\Ccal_1}(\gamma^l)),
\end{align*}
which checks 
$\lim_{l\rightarrow +\infty} \gamma^l = P_{\Ccal_1 \cap \Ccal_2}(\gamma^0) = \gamma^*.$

>>>>

\subsection{Discrete Optimal Transport}
We consider two discrete probability measures $\mu^k \in \IR_{+*}^{n_k}$.
Let us define the two following linear operators
\begin{align*}
A_1 &: \begin{cases}
\IR^{n_1 n_2} \rightarrow \IR^{n_1} \\
(A_1 x)_i = \sum_j x_{i,j}
\end{cases} &
A_2 &: \begin{cases}
\IR^{n_1 n_2} \rightarrow \IR^{n_2}\\
(A_2 x)_j = \sum_i x_{i,j},
\end{cases}
\end{align*}
as well as the linear  constraint sets
\begin{align*}
\Ccal_k &= \left\{ \gamma\in\IR^{n_1 n_2} \mid A_k \gamma = \mu^k \right\}.
\end{align*}
Given a cost matrix $c$, where $c_{ij}$ represents the cost of moving mass $\mu^1_i$ to $\mu^2_j$,  the optimal transport problem corresponds to the estimation of an optimal transport matrix $\gamma$ solution of:
$$\min_{\gamma\in\Ccal_1\cap \Ccal_2\cap \IR^{n_1 n_2}_+} \langle c,\gamma\rangle:=\sum_{i,j}c_{i,j}\gamma_{i,j}.$$
This is a linear programing problem whose resolution is intractable for large scale problems.

@@

\subsection{Sinkhorn's algorithm}
Iterative Bregman projections onto $\Ccal_1$ and $\Ccal_2$ converge to a point in the intersection $\Ccal_1 \cap \Ccal_2$ \cite{bregman67}. Hence, the so-called Sinkhorn algorithm \cite{sinkhorn64} can be considered to compute the regularized  transport matrix:
\begin{align*}
\gamma^0 &= e^{-c/\epsilon} &
\gamma^{l+1} = P_{\Ccal_2}(P_{\Ccal_1}(\gamma^l)),
\end{align*}
which checks 
$\lim_{l\rightarrow +\infty} \gamma^l = P_{\Ccal_1 \cap \Ccal_2}(\gamma^0) = \gamma^*.$
